% Modern one-page-ish academic CV (LaTeX)
\documentclass[11pt]{article}

\usepackage[margin=1.7cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=MidnightBlue,
  citecolor=MidnightBlue
}

\definecolor{MidnightBlue}{HTML}{0F4C81}
\definecolor{Muted}{HTML}{334155}
\definecolor{Rule}{HTML}{CBD5E1}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\titleformat{\section}{\large\bfseries\color{MidnightBlue}}{}{0em}{}[\vspace{2pt}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\newcommand{\tightlist}{\setlist[itemize]{leftmargin=*, nosep, topsep=2pt}}
\newcommand{\role}[2]{\textbf{#1}\hfill\textcolor{Muted}{#2}\\}
\newcommand{\subrole}[2]{\textit{#1}\hfill\textcolor{Muted}{#2}\\}

\begin{document}

% Header
\begin{tabularx}{\linewidth}{@{}X r@{}}
  {\Huge \textbf{Leandro Di Bella}} & {\textcolor{Muted}{Brussels, Belgium}}\\
  {\textcolor{Muted}{PhD candidate (ETRO, VUB) \;\textbullet\; Autonomous Perception \;\textbullet\; Tracking \;\textbullet\; Vision-Language}} & \\
\end{tabularx}

\vspace{4pt}
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \href{mailto:leandro.dibella@gmail.com}{\faEnvelope\; leandro.dibella@gmail.com} \quad
  \href{https://github.com/leandro-svg}{\faGithub\; leandro-svg} \quad
  \href{https://scholar.google.de/citations?user=f7IDHsgAAAAJ&hl=en}{\faGraduationCap\; Google Scholar} \quad
  \href{https://orcid.org/0009-0000-1731-7205}{\faIdBadge\; ORCID} \quad
  \href{https://www.linkedin.com/in/leandro-di-bella-62381413b/}{\faLinkedin\; LinkedIn}
  & \href{https://mappx.app}{\faLink\; mappx.app}\\
\end{tabularx}

\vspace{6pt}
\hrule height 0.6pt \vspace{10pt}

\section*{Summary}
Computer vision \& generative AI for autonomous perception in driving and drones. Focus on deployable systems with \textbf{temporal consistency}, \textbf{robustness under distribution shift}, and \textbf{real-time constraints}. Interests: multi-object tracking (3D MOT), vision-language grounding/reasoning, and motion forecasting.

\section{Education}
\role{PhD in Engineering Sciences (AI \& Computer Vision) \textemdash\ ETRO, Vrije Universiteit Brussel (VUB)}{2023--Present}
\subrole{Research: autonomous perception, tracking, vision-language, forecasting}{Brussels, Belgium}

\role{Advanced Master in Industrial \& Technological Management \textemdash\ Solvay Brussels School}{2025--2027 (ongoing)}

\role{M.Sc. Electrical Engineering (Information Technology Systems) \textemdash\ Bruface (ULB/VUB)}{2020--2023}

\role{B.Eng. \textemdash\ Bruface (ULB/VUB)}{2017--2020}

\section{Experience}
\role{Founder \textemdash\ Mappx}{Aug 2025--Present}
\tightlist
\begin{itemize}
  \item Built a map-centric social travel app (Flutter) with a FastAPI backend and PostgreSQL.
  \item Deployed and operated cost-effective infrastructure using Azure and Firebase.
\end{itemize}

\role{Intern \textemdash\ MACQ Mobility}{Aug 2022--Oct 2022}
\tightlist
\begin{itemize}
  \item Developed and integrated instance segmentation on NVIDIA Jetson TX2 (Python/C++).
\end{itemize}

\role{Teaching Assistant \textemdash\ Vrije Universiteit Brussel (VUB)}{\textasciitilde 2022--2025}
\tightlist
\begin{itemize}
  \item Machine Learning and Big Data Processing (2.5 years).
\end{itemize}

\section{Selected Publications}
\tightlist
\begin{itemize}
  \item \textbf{HybridTrack}: A Hybrid Approach for Robust Multi-Object Tracking. \textit{IEEE RA-L / ICRA}. (2025)
  \item \textbf{ReferGPT}: Towards Zero-Shot Referring Multi-Object Tracking. \textit{CVPR Workshops}. (2025)
  \item \textbf{DeepKalPose}: Temporally Consistent Monocular Vehicle Pose Estimation. \textit{Electronics Letters}. (2024)
  \item \textbf{ChronoFusion}: Spatio-Temporal Super-Resolution via Graph VAEs and Gated Fusion. \textit{EUVIP}. (2025)
\end{itemize}

\section{Projects}
\role{Embedded AI \textemdash\ Real-Time Instance Segmentation with TensorRT/ONNX}{2023}
\tightlist
\begin{itemize}
  \item Optimized SparseInst and YOLOv7 for real-time deployment on NVIDIA edge devices using CUDA/TensorRT.
\end{itemize}

\section{Skills}
\textbf{Programming:} Python, C++, CUDA, PyTorch, Flutter/Dart, FastAPI\\
\textbf{Platforms/Tools:} Docker, Azure, Firebase, GitHub, VS Code, PostgreSQL\\
\textbf{Research:} Multi-object tracking, autonomous perception, vision-language models, forecasting

\section{Languages}
French (Native) \;\textbullet\; English (C1) \;\textbullet\; Dutch (B1)

\section{Supervision}
Supervised 6 Master’s theses (topics: coral reef fish ID; monocular 3D detection; drone navigation in GNSS-degraded settings; pruning/quantization; pedestrian intention via VLM action models; pose estimation on embedded devices).

\vspace{4pt}
{\small\textcolor{Muted}{Last updated: \today}}

\end{document}
